Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-01-12 fertile.Rmd
resolving issue #15/17 (references)

@@

>>>>

R OpenSci also has a discussion of code review practices where users commented. Not too much that was helpful from here (just a few odd comments):
https://discuss.ropensci.org/t/how-do-you-review-code-that-accompanies-a-research-project-or-paper-help-ropensci-plan-a-community-call/1321/43

@@

### represtools

https://pirategrunt.com/represtools/

Has basic utility functions to support reproducibile research
• Gather
• Cook
• Analyze
• Present

### orderly

https://github.com/vimc/orderly

Focuses on automating a series of basic steps in the prodcess of writing analyses.
• Tracks inputs
• Stores multiple versions of an analysis (unclear whether this is different stages?)
• Track outputs
• Create analyses that depend on the outputs of previous analyses
• You have to declare what you're going to use and create BEFORE you start the analysis

### workflowr

https://f1000research.com/articles/8-1749

Aims to instill a particular workflow that helps make projects more reproducible.

• Version control (git)
• Literate programming (Rmd)
• Automatic checks & safeguards (seemingly related to whether different files in a project have been published on git, and not actually to do with code practices)
• Sharing code / results via browsable website

### checkers

https://github.com/ropenscilabs/checkers

• A framework for reviewing analysis projects
• Seems to be something run after-the-fact
• Currently a work in progress and not passing checks (as of Jan 2019)
• Can create custom checks
• Checks include:
 - Comments
 - Good coding style (lintr)
 - Use of version control
 - Whether preferred packages are used
